Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-11-13 manuscript.Rmd
Fix typos

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET and NRLINE for social cohesion with all events
supports our first hypothesis that event activity is coupled with online social
cohesion. The frequency of all events are thus associated with
greater shared trajectories with social cohesion than would be expected by
chance. This could be due to a conflation of the different kinds of events. However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis. In addition to the significant DET and NRLINE metrics seen in the all events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship. This may be a reflection of citizens' reaction to events that are positively influential to their cause. An act of concession by the government or aid from another country may have led to an increase in moral or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale. By contrast, negative event frequency showed weak coupling, counter to our third hypothesis. Although the significant reuslt for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time. Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter in the following days to report post-hoc what had happened. Further text analysis should be conducted to decipher the underlying tone of the tweets.

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size
by 1,690 samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There are no longer a signficant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequncy of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social coheison online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). But the significant ENTR metric suggests that there is more variablity in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.

>>>>

## Cross-Recurrence Quantification Analysis
### Syria as Target
The significant result of DET and NRLINE for social cohesion with all events
supports our first hypothesis that event activity is coupled with online social
cohesion. The frequency of all events are thus associated with
greater shared trajectories with social cohesion than would be expected by
chance. This could be due to a conflation of the different kinds of events. However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis. In addition to the significant DET and NRLINE metrics seen in the all events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship. This may be a reflection of citizens' reaction to events that are positively influential to their cause. An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale. By contrast, negative event frequency showed weak coupling, counter to our third hypothesis. Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time. Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter in the following days to report post-hoc what had happened. Further text analysis should be conducted to decipher the underlying tone of the tweets.

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size
by 1,690 samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). But the significant ENTR metric suggests that there is more variability in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.
